### 2009-09-17 trunk/latex/paper1/contents.tex
paper

\section{Introduction}

@@

Unfortunately there are few systems with known reference decompositions.
Furthermore, because it is costly to obtain reference decompositions
\cite{Koschke2000}, there are few empirical studies about software clustering
algorithms, most of them based on a couple of small and medium systems
\cite{Anquetil1999,Maqbool2007,Bittencourt2009}.

@@

The remaining sections are organized as follows. .... Section 2, ...

@@

\section{Software Networks}

The implementation of a software system can be viewed as a network of
interacting components. In a object-oriented system, for example, classes
interact with other classes through mechanisms such as inheritance and
aggregation. By abstract the particular mechanisms of interaction, it is
possible to build a network of dependencies between components, represented as a
directed graph. This kind of network is the input for many software clustering
algorithms \cite{Mancoridis1998,Anquetil1999,Tzerpos2000,Andritsos2005}.

In this paper we will study networks of dependencies between classes in
object-oriented systems. We will call any such a network a \emph{software
network}.

@@

Network theory research studies general properties of many types of networks by
using statistical analysis. In the last decade, it has been found that many
networks arising from sociology, biology, technology and other domains present
remarkable structural similarities. It has been shown that, in these networks,
the distribution of vertex degrees is a power law, i.e., the number of vertices
connected to $k$ edges, N($k$), is proportional to $k^{\-gamma}$, where $\gamma$
is a positive constant. These networks are called scale-free networks.

Network theory has been applied to software networks and it was shown that they
are also scale-free networks \cite{Myers2003,Valverde2003}.

@@

\section{Network Models}

Many models were proposed to explain the formation of scale-free networks. These
models are simple algorithms that can be proven, either formally or empirically,
to synthesize networks that are scale-free. Most models, though, do not account
for modular structure, a feature present in some networks, in particular
software networks. In this section we present three models that synthesize
directed networks with built-in modular decompositions: BCR+, CGW and LR.

@@

\begin{itemize}
\item number of vertices, $n$;
\item a graph, $G$;
\item three probabilities, $p$, $q$, and $r$, such as $p + q + r = 1$;
\item a probability, $mu$;
\item two real numbers, $\din$ and $\dout$.
\end{itemize}

In a network with modules, one can define a module dependency graph (MDG) as a
graph where the two following conditions hold:

\begin{itemize}
\item each vertex represents a module in the original network; 
\item there is an edge from $M_1$ to $M_2$ in the MDG only if there is an edge
from $v_1$ to $v_2$ in the original network, where $v_1 \in M_1$ and $v_2 \in
M_2$.
\end{itemize}

The BCR+ model synthesizes networks whose MDG is equal to $G$ by adding vertices
and edges to an initial network until it reaches $n$ vertices. The initial
network is isomorphic to $G$: it contains one vertex for each module and one
edge for each edge in $G$, connecting vertices whose corresponding modules are
connected. Thus, the MDG for the generated network is equal to $G$ from the very
beginning.

After that, the algorithm consists of successive applications of one out of
three operations on the network: (1) adding a vertex with an outgoing edge; (2)
adding a vertex with an ingoing edge; (3) adding a edge between existing
vertices. In operation 3, the edge can connect either vertices that belong
to the same module or vertices in distinct modules.

The choice of the vertices that will be connected by a new edge, although
non-deterministic, is not fully random. The probability that a particular vertex
v is choosen, P($v$), is proportional to a function of the in-degree or the
out-degree of the node. We say that we choose a vertex within a set of vertices
$S$ according to a function f if

$$
  P(v) ~=~ \frac{ \mathrm{f}(v) }{ \displaystyle\sum_{v \in S} \mathrm{f}(v) }.
$$

The denominator is a normalizing factor that assures that the probabilities sum
to 1.

Before we present the algorithm in detail, using pseudo-code, we must define
some functions:

%Let V be the set of vertices in the network being generated. This
%set grows as the algorithm is executed. Being v a vertex, we define the
%following three functions:

\begin{itemize}

\item \textbf{in-degree(v)}: the number of edges that enter the vertex v;

\item \textbf{out-degree(v)}: the number of edges that leave the vertex v;

\item \textbf{module(v)}: the module to which the vertex v belongs;

\item \textbf{out-neighbors(v)}: the set of all vertices that are connected to
the vertex v by an edge starting in v.

\item \textbf{same-module(v)}: the set of all vertices that are in the same
module as the vertex v, except for v itself and vertices in out-neighbors(v).

\item \textbf{other\_modules(v)}: the set of all vertices that are in modules
that are connected to v's module (in the graph G) by an edge starting in v's
module, except for vertices in out-neighbors(v).

\end{itemize}

After the initial network is created, the algorithm proceeds as follows:

\begin{figure*}
\begin{verbatim}
while the number of nodes in the network is less than n:
  choose one of the operations according to probabilities (p, q, r)
  operation 1: (add a vertex with an outgoing edge)
    choose a vertex w within V according to f(x) = din + in-degree(x)
    add a new vertex, v, to module(w)
    add an edge from v to w
  operation 2: (add a vertex with an ingoing edge)
    choose a vertex w within V according to f(x) = dout + out-degree(x)
    add a new vertex, v, to module(w)
    add an edge from w to v
  operation 3: (add an edge between two existing vertices)
    choose a vertex v within V according to f(x) = dout + out-degree(x)
    choose a case according to probabilities (mu, 1 - mu)
    case 1: (distinct modules)
  	  choose a vertex w within other\_modules(v) according to f(x) = din + in-degree(x)
      add an edge from v to w
    case 2: (same module)
      choose w within same-module(v) according to f(x) = din + in-degree(x)
      add an edge from v to w
\end{verbatim}
\end{figure*}

We can see that the probabilities $p$, $q$, and $r$ control how often each
operation is performed. Because the operation associated with probability $r$
does not add any vertices, greater values of $r$ imply more edges in the
resulting network. It is easy to see that nodes connected to many ingoing edges
are more likely to get another ingoing edge. The parameter $\din$ can alleviate
the handicap by providing a ``base in-degree'' that is applied to all vertices
when computing the probabilities. Consider two vertices, $v_1$ with in-degree 4,
and $v_2$ with in-degree 8. If $\din = 0$, $v_2$ is twice more likely to receive
a new incoming edge; if, otherwise, $d\in = 4$, $v_2$ is only $\frac{3}{2}$ more
likely to receive the edge. The same reasoning applies to $\dout$.

The parameter $mu$ controls the proportion of edges between vertices in distinct
modules. Lower values of $mu$ lead to networks with weakly coupled modules.

The BCR+ model is a growth model, meaning that the network is created vertex by
vertex, growing from an initial network. It can, therefore, simulate the
evolution of a software network. Moreover, it can simulate the evolution of a
software system subject to constraints in module interaction, as is the case
with top-down system design methodologies CITE.

%* Add a node with ongoing edge. With probability p, a new vertex is added to the network, together with an
%edge from the new vertex to an existing vertex, chosen preferentially according
%to .... Considering din = 0, this means that a vertex with indegree = 8 is
%twice more likely to receive the edge than a vertex with indegree = 4. The
%parameter din can be used to alleviate the handicap. (If din = 4, the first
%vertex will only be 3/2 more likely to receive the edge). The new vertex is
%put on the same cluster as the old vertex.
%
%* Add a node with ingoing edge. With probability q, a new vertex is added to the network, together with an
%edge from an existing vertex, chosen preferentially accordingly to dout +
%outdegree, to the new vertex. The new vertex is put on the same cluster as the
%old vertex. This case is similar to the previous case.
%
%* Add an edge. With probability r, a new edge is added between two vertices, v and w. v is
%chosen according to .... After that, with prob X, w is chosen from one of the
%modules connected to v's module, else it's chosen from v's own module. In any
%case, the exact choice is made according to ...
%
%It's a growth model, that is, it can take as input an existing network and
%evolve it.
%
%TODO: Argument: why the imposed modules are natural modules?

@@

\begin{itemize}
\item Number of vertices, n;
\item Number of modules, m;
\item Probabilities $p_1, p_2, p_3, p_4$, summing to 1;
\item Natural numbers $e_1, e_2, e_3, e_4$;
\item Constant $\alpha$, with $\alpha \ge -1$
\end{itemize}

Just like BCR+, this is a growth model. Its initial network is composed of two
vertices belonging to the same module and a directed edge between them. The
remaining $m - 1$ modules are initially empty.

After that, the algorithm consists of successive applications of one out of four
operations on the network, which are chosen according to probabilities $p_1, p_2,
p_3, and p_4$: 
(1) adding a vertex with $e_1$ outgoing edges; 
(2) adding $e_2$ edges;
(3) rewiring $e_3$ edges;
(4) removing $e_4$ randomly chosen edges.

Whenever an edge is added from a vertex $v$ to a vertex $w$ (operations 1, 2,
and 3), $v$ is chosen randomly, and $w$ is chosen according to the following
probability function:

$$
  P_v(w) ~=~ \frac{ f_v(w) }{ \displaystyle\sum_{w \in S, f_v(w)} },
$$

where

$$
f_v(w) = \left\{
\begin{array}{ll}

1 + degree(w) \cdot (1 + \alpha) &  \mathrm{if}\ module(w) = \\%= module(v) \\
                                 &  = module(v) \\
1 + degree(w) & \mathrm{otherwise}
\end{array}
\right.
$$

@@

Because the original paper did not provide an implementation for the model, we
now present the pseudo-code for our implementation:

\begin{figure*}
\begin{verbatim}
  operation 1: (adding a vertex with e1 outgoing edges)
    create a new vertex v and add it to a randomly chosen module
    repeat e1 times:
      choose a vertex w according to f\_v(w)
      add an edge from v to w

  operation 2: (adding e2 edges)
    repeat e2 times:
      choose a vertex v randomly
      choose a vertex w according to f\_v(w)
      add edge from v to w

  operation 3: (rewiring e3 edges)
    repeat e3 times:
      choose a vertex v randomly
      choose an edge e randomly within edges that start in v
      choose w according to f\_v(w)
      remove e
      add an edge from v to w

  operation 3: (removing e4 edges)
    repeat e4 times:
      remove a randomly chosen edge
\end{verbatim}
\end{figure*}

Unlike BCR+, this model does not allow constraints on the connection between
modules, however it accounts for the rewiring and the removal of edges.

@@

The sizes of the modules are selected from a power law distribution with
exponent $-\beta$. The mixing parameter, $\mu$ is the proportion of edges in the
network that connect vertices from distinct modules. In this model, some
combinations of parameter values are unfeasible. For example, if $n = 100$ then
$min_m$ cannot be 60 (otherwise there would be modules smaller than the minimum
module size).

@@

\section{Characterization of Software Networks}

Our research hypothesis is that at least one of the presented models can
synthesize networks that resemble software networks. A central issue, thus, is
how to measure similarity between networks. In order to be useful, a similarity
metric must be able to differentiate between software and non-software networks.
In this section we present such a metric, together with an experiment that
evaluates its usefulness by applying it to both software and non-software
networks. %Then we show a classification model

@@

CITE igraph

@@

By counting how many times each triad appears in a network, one can build a
triad concentration profile (TCP), which is a vector with 13 numbers that
summarize the local structure of the network. Figure \ref{fig:profiles} shows
the TCP for networks from distinct domains.

@@

$$
\mathrm{sim}(a, b) ~=~ \mathrm{cor}(\mathrm{TCP}(a), \mathrm{TCP}(b))\mathrm{,}
$$

@@

$$
\mathrm{S\mbox{-}score}(a) = \frac{
\displaystyle\sum_{s \in S} \mathrm{sim}(a, s)
}{|S|} \mathrm{,}
$$

@@

Then we measured the S-score for each non-software network. The majority of the
networks (X\%) had a S-score lower than 0.83, which is the lowest S-score for
software networks in the sample. Some networks, showing friendship between
students, showed negative S-score, meaning that they are very different from
software networks.

Two networks, though, showed high S-score, above 0.83. The network of links
between blogs on politics showed S-score 0.97. The neural network of the worm
C. Elegans also showed a high S-score (0.88). Further investigation is needed
in order to discover the reasons behind these high S-scores and whether
auxiliary metrics can differentiate these networks from software networks.

@@

\section{Evaluation of Network Models}
% v.  differentiate, differ; distinguish; contrast; discern

@@

\begin{itemize}
\item $p, q, r \in \{0.0, 0.2, 0.4, 0.6, 0.8, 1.0\}$, with $p + q + r = 1$ and
$p + q > 0$;
\item $\din, \dout \in \{0, 1, 2, 3, 4\}$;
\item $\mu \in \{0.0, 0.2, 0.4, 0.6\}$.
\end{itemize}

@@

\begin{table}
\caption{Rules for predicting the classification of a synthetic network. S
stands for software-like and N stands for non software like.}
\centering
\begin{tabular}{|l|l|l|}
\hline
Model & Rule & Accuracy \\
\hline 
\hline
\multirow{2}{*}{BCR+}
     & $\alpha \ge 0.7 \Rightarrow S$ & \multirow{2}{*}{82.4\%}  \\ 
     & $\alpha < 0.7 \Rightarrow N$ & \\ 
\hline
\multirow{2}{*}{CGW}
     & $p_1 \ge 0.5 \Rightarrow S$ & \multirow{2}{*}{82.3\%} \\  
     & $p_1 < 0.5 \Rightarrow N$ & \\  
\hline
\multirow{2}{*}{LF}   
     & $\gamma \ge 2.44 \Rightarrow S$ & \multirow{2}{*}{78.9\%} \\ 
     & $\gamma < 2.44 \Rightarrow N$ & \\ 
\hline
\end{tabular}
\label{tab:rules}
\end{table}

@@

\section{Conclusion and Future Work}
% revised 2009-09-03

@@

\begin{itemize}
\item 5 friendship networks from Facebook \cite{Traud2008};
\item 3 electronic circuit networks \cite{Milo2004};
\item 4 word adjacency networks \cite{Milo2004};
\item 3 protein structure networks \cite{Milo2004};
\item 2 social networks of positive sentiment \cite{Milo2004};
\item 43 metabolic networks \cite{Jeong2000};
\item Protein interaction network for yeast \cite{Jeong2001};
\item Links between political blogs \cite{Adamic2005};
\item Neural network of C Elegans \cite{Watts1998};
\item Network ``beta3sreduced'' (unknown source);
\item Network ``czech'' (unknown source);
\item Network ``ecoli-metabolic'' (unknown source).
\end{itemize}

>>>>

\section{Introduction} \label{sec:introduction}

@@

Unfortunately there are few systems with known reference decompositions.
Furthermore, because such decompositions are costly do obtain
\cite{Koschke2000}, there are few empirical studies about software clustering
algorithms, most of them based on a couple of small and medium systems
\cite{Anquetil1999,Maqbool2007,Bittencourt2009}.

@@

The remaining sections are organized as follows. 
Section \ref{sec:swnets}...
Section \ref{sec:models}...
Section \ref{sec:characterization}...
Section \ref{sec:evaluation}...
Section \ref{sec:conclusion}...

@@

\section{Software Networks} \label{sec:swnets}
% TODO: consider merging with introduction

At the implementation level, a software system can be viewed as a network of
interacting components. In a object-oriented system, for example, classes
interact with other classes through mechanisms such as inheritance and
aggregation. By abstracting the particular mechanisms of interaction, it is
possible to build a network of dependencies between components, represented as a
directed graph. This kind of network is the input for many software clustering
algorithms \cite{Mancoridis1998,Anquetil1999,Tzerpos2000,Andritsos2005}.

In this paper we will study networks of dependencies between classes in
object-oriented systems. We will call any network of this kind a \emph{software
network}. Software networks can be studied by network theory.

@@

Network theory researchers study general properties of many types of networks by
using statistical analysis. In the last decade, it has been found that many
networks arising from sociology, biology, technology and other domains present
remarkable structural similarities. It has been shown that, in these networks,
the distribution of vertex degrees is a power law, i.e., the number of vertices
connected to $k$ edges is proportional to $k^{\-\gamma}$, where $\gamma$ is a
positive constant. These networks are called scale-free networks.

Network theory has been applied to software networks and it was shown that they
are also scale-free networks \cite{Myers2003,Valverde2003}. Because of this
fact, it is possible to take advantage of network theory tools and techniques
when studying the structure of software systems in general.

@@

\section{Network Models} \label{sec:models}

Many models were proposed to explain the formation of scale-free networks. These
models are algorithms that can be proven, either formally or empirically, to
synthesize networks that are scale-free. Most models, though, do not account for
modular structure. In this section we present three models that synthesize
directed networks with built-in modular decompositions: BCR+, CGW and LF.

@@

\begin{itemize}
\item number of vertices, $n$;
\item a directed graph of modules, $G$;
\item three probabilities, $p_1$, $p_2$, and $p_3$, summing to 1;
\item constant $\mu$, with $0 \le \mu \le 1$;
\item base in-degree, $\din$;
\item base out-degree, $\dout$.
\end{itemize}

The graph $G$ contains one vertex for each module that will be created and
determines a ``supply'' relationship between modules. We say that module $M_2$
is a supplier of module $M_1$ if, and only if, $G$ contains an edge from $M_1$
to $M_2$.

Networks generated by the model can contain both internal edges and external
edges. An internal edge connects two vertices in the same module. An external
edge connects vertices in distinct modules. In this model, an external edge from
a vertex $v_1 \in M_1$ to a vertex $v_2 \in M_2$ is only allowed if $M_2$ is a
supplier of $M_1$.

The parameter $\mu$ controls the proportion external edges in the network. Lower
values of $\mu$ lead to networks with fewer external edges and, therefore, to
weakly coupled modules.

First the model creates an initial network in which each module contains exactly
one vertex. Then all allowed external edges are added. Finally, the networks is
modified by sucessive choices between three operations that add vertices or
edges to the network, until it reaches $n$ vertices. Each time, the probability
of choosing the $i$-th operation is $p_i$.

Before describing the operations, some definitions are needed. The expression
in-degree($x$) means the number of edges that enter the vertex $x$;
out-degree($x$), likewise, is the number of edges that leave vertex $x$. The
expression ``to choose a vertex according to f(x)'' means that the probability
of choosing a vertex $x$ is given by the following probability function:

$$
  \mathrm{P}(x) ~=~ \frac{ \mathrm{f}(x) }
  { \displaystyle\sum_{i} \mathrm{f}(i) }
$$

(the denominator is a normalizing factor, so the sum of probabilities is 1).

The three operations are described next:

\begin{enumerate}

\item \emph{Adding a vertex with an outgoing edge}. An existing vertex, $w$, is
chosen according to $\mathrm{f}(x) = \din + \mathrm{in\mbox{-}degree}(x)$. A new
vertex, $v$, is added to the module of $w$, together with an edge from $v$ to
$w$.

\item \emph{Adding a vertex with an ingoing edge}. An existing vertex, $w$, is
chosen according to $\mathrm{f}(x) = \dout + \mathrm{out\mbox{-}degree}(x)$. A
new vertex, $v$, is added to the module of $w$, together with an edge from $w$
to $v$.

\item \emph{Adding an edge between existing vertices}. A vertex, $v$, is choosen
from the network according to $\mathrm{f}(x) = \dout +
\mathrm{out\mbox{-}degree}(x)$.  Then an edge is added from vertex $v$ to an
existing vertex $w$, which is chosen according to one of the following cases:

\begin{enumerate}
  \item with probability $\mu$, $w$ is chosen among vertices in modules that are
  suppliers of the module of $v$;
  \item with probability $1 - \mu$, $w$ is chosen among vertices in that same
  module as $v$.
\end{enumerate}

\end{enumerate}

It is easy to see that nodes with high in-degree are more likely to receive new
ingoing edges. The parameter $\din$ can reduce this bias by providing a base
in-degree that is applied to all vertices when computing the probabilities.
Consider two vertices, $v_1$ with in-degree 4, and $v_2$ with in-degree 8. If
$\din = 0$, $v_2$ is twice more likely to receive a new incoming edge; if,
otherwise, $\din = 4$, $v_2$ is only $\frac{3}{2}$ more likely to receive the
edge. The same reasoning applies to $\dout$.

The BCR+ model is a growth model, meaning that the network is created vertex by
vertex, growing from an initial network. It can, therefore, simulate the
evolution of a software network. Moreover, it can simulate the evolution of a
software system subject to constraints in module interaction, as is the case
with top-down system design methodologies.

%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*

@@

\begin{itemize}
\item number of vertices, $n$;
\item number of modules, $m$;
\item probabilities $p_1, p_2, p_3, p_4$, summing to 1;
\item natural numbers $e_1, e_2, e_3, e_4$;
\item constant $\alpha$, with $\alpha \ge -1$.
\end{itemize}

Because the model is described in detail in the original paper, only an
intuitive notion of the meaning of the parameters is provided here. This model
is similar to BCR+ in which it grows an initial network by sucessive
applications of operations. In this case, there four operations, which are
chosen according to probabilities $p_1$, $p_2$, $p_3$, and $p_4$:

\begin{enumerate}
\item adding a vertex with $e_1$ outgoing edges; 
\item adding $e_2$ edges;
\item rewiring $e_3$ edges;
\item removing $e_4$ randomly chosen edges.
\end{enumerate}

@@

%Unlike BCR+, this model does not allow constraints on the connection between
%modules, however it accounts for the rewiring and the removal of edges.

%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*%*

@@

The sizes of the modules are selected from a power law distribution with
exponent $-\beta$. The mixing parameter, $\mu$, is the proportion of edges in the
network that connect vertices from distinct modules. In this model, some
combinations of parameter values are unfeasible. For example, if $n = 100$ then
$min_m$ cannot be 60 (otherwise there would be modules smaller than the minimum
module size).

@@

\section{Characterization of Software Networks} \label{sec:characterization}

Our research hypothesis is that at least one of the presented models can
synthesize networks that resemble software networks. A central issue, thus, is
how to measure similarity between networks. In order to be useful, a similarity
metric must be able to differentiate between software and non-software networks
(e.g., biologic networks). % TODO: whooo, too fast here.
In this section we present such a metric, together
with an experiment that evaluates its usefulness by applying it to both software
and non-software networks. %Then we show a classification model

@@

@@

By counting how many times each triad appears in a network, one can build a
triad concentration profile (TCP), which is a vector with 13 numbers that
summarize the local structure of the network. Figure \ref{fig:profiles} shows
the TCP for networks from two distinct domains.

@@

$$
\mathrm{similarity}(a, b) ~=~ 
  \mathrm{cor}(\mathrm{TCP}(a), \mathrm{TCP}(b))\mathrm{,}
$$

@@

$$
\mathrm{S\mbox{-}score}(a) = \frac{
\displaystyle\sum_{s \in S} \mathrm{similarity}(a, s)
}{|S|} \mathrm{,}
$$

@@

Then we measured the S-score for each non-software network. The majority of the
networks (97.0\%) had a S-score lower than 0.83, which is the lowest S-score for
software networks in the sample. Some networks, e.g., the friendship networks
between students, showed negative S-score, meaning that they are very different
from software networks.

Two networks, though, showed high S-score, above 0.83. The network of links
between blogs on politics showed S-score 0.97. The neural network of the worm C.
Elegans also showed a high S-score (0.88). Further investigation is needed in
order to discover the reasons behind the high values and whether auxiliary
metrics can differentiate these networks from software networks.

@@

\section{Evaluation of Network Models} \label{sec:evaluation}
% v.  differentiate, differ; distinguish; contrast; discern

@@

\begin{itemize}
\item $p_1, p_2, p_3 \in \{0.0, 0.2, 0.4, 0.6, 0.8, 1.0\}$, with $p + q + r = 1$ and
$p + q > 0$;
\item $\din, \dout \in \{0, 1, 2, 3, 4\}$;
\item $\mu \in \{0.0, 0.2, 0.4, 0.6\}$.
\end{itemize}

@@

\begin{table}
\caption{Rules for predicting the classification of a synthetic network. S
stands for software-like and N stands for non software like.}
\centering
\begin{tabular}{|l|l|l|}
\hline
Model & Rule & Accuracy \\
\hline 
\hline
\multirow{2}{*}{BCR+}
     & $p_1 \ge 0.7 \Rightarrow S$ & \multirow{2}{*}{82.4\%}  \\ 
     & $p_1 < 0.7 \Rightarrow N$ & \\ 
\hline
\multirow{2}{*}{CGW}
     & $p_1 \ge 0.5 \Rightarrow S$ & \multirow{2}{*}{82.3\%} \\  
     & $p_1 < 0.5 \Rightarrow N$ & \\  
\hline
\multirow{2}{*}{LF}   
     & $\gamma \ge 2.44 \Rightarrow S$ & \multirow{2}{*}{78.9\%} \\ 
     & $\gamma < 2.44 \Rightarrow N$ & \\ 
\hline
\end{tabular}
\label{tab:rules}
\end{table}

@@

\section{Conclusion and Future Work} \label{sec:conclusion}
% revised 2009-09-03

@@

\begin{itemize}
\item 5 friendship networks from Facebook \cite{Traud2008}
\item 3 electronic circuit networks \cite{Milo2004}
\item 4 word adjacency networks \cite{Milo2004}
\item 3 protein structure networks \cite{Milo2004}
\item 2 social networks of positive sentiment \cite{Milo2004}
\item 43 metabolic networks \cite{Jeong2000}
\item Protein interaction network for yeast \cite{Jeong2001}
\item Links between political blogs \cite{Adamic2005}
\item Neural network of C Elegans \cite{Watts1998}
\item Network ``beta3sreduced'' (unknown source)
\item Network ``czech'' (unknown source)
\item Network ``ecoli-metabolic'' (unknown source).
\end{itemize}
